Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-18 Publications/2013-IPMI/Latex/045-Experiments.tex

\section{Data and experiments}
\label{sec:experiments}
%
\subsection{Shape prior}
%
As described in \autoref{sec:introduction}, the general situation in
the connectivity pipelines consists of having 
a reliable segmentation obtained from the high resolution \ac{t1} 
reference image. Therefore, a precise location of the tissue interfaces
of interest is available in a reference space. Given that the anatomical 
reference segmentation is beyond the scope of this manuscript, we simply 
rely on the shape priors obtained from the models.

%
\subsection{Synthetic gray-scale data}
%
The first, toy example is inspired by a problem shown for coupled CSF/GM 
and GM/WM segmentation in \cite{MacDonald2000}. \textbf{FIXME description of the model, expected difficulties (PVE -- lack of contour in sulcus), and how proposed model is expected to cope with this}.

%
\subsection{Simulated diffusion data}
%
In order to demonstrate the specific functionality of the proposed
methodology and characterize its possibilities with diffusion data, we developed a
synthetic model and simulated its corresponding \ac{dwi}
raw signal as described in \citep{tuch_q-ball_2004}.

>>>>

\section{Data and experiments}
\label{sec:experiments}
%
\subsection{Shape prior}
%
As described in \autoref{sec:introduction}, the general situation in
the connectivity pipelines consists of having 
a reliable segmentation obtained from the high resolution \ac{t1} 
reference image. Therefore, a precise location of the tissue interfaces
of interest is available in a reference space. Given that the anatomical 
reference segmentation is beyond the scope of this manuscript, we simply 
rely on the shape priors obtained from the models.
%
\subsection{Synthetic gray-scale data}
%
The first, toy example is inspired by a problem shown for coupled CSF/GM and GM/WM segmentation in \cite{MacDonald2000}. The authors note that ``partial volume effects blur the distinction between closely adjacent surfaces in deep sulci, leading to a well-known segmentation error in which the deeper reaches of sulci are not penetrated by the putative surface model.'' This problem is aggravated in DWI, since the resolution tends to be worse compared to the anatomical images considered in \cite{MacDonald2000}. They test their coupled segmentation algorithm on an image, ``representing a sulcus in which the distinction between opposing banks of the sulcus has been obscured by partial volume.''  As illustrated, conventional single surface segmentation of the CSF/GM boundary misses to capture the sulcus in its full depth. With our proposed model, we expect the joint segmentation-registration to be driven largely by the inner, GM/WM contour that exhibits sufficient contrast and lesser partial volume effects.
%
\subsection{Simulated diffusion data}
%
In order to demonstrate the specific functionality of the proposed
methodology and characterize its possibilities with diffusion data, we developed a
synthetic model and simulated its corresponding \ac{dwi}
raw signal as described in \citep{tuch_q-ball_2004}.
